Risk Perceptions for Wearable Devices

### 2015-12-19 paper.tex
Fix broken section reference (it was a ref to start of Sec 3)
Took full pass, fixed a lot of typos

\begin{document}
\title{Risk Perceptions for Wearable Devices}
%\numberofauthors{1}
%\author{
% \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
%   \vspace{0.5em}
%   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
%   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
%}

\numberofauthors{1}
\author{
 \alignauthor Anonymous\\
   \vspace{0.5em}
   \affaddr{Some Place}
}
\maketitle

\begin{abstract}
\indent\indent Wearable devices, or ``wearables,'' bring great benefits but also potential risks that could expose users' activities without their awareness or consent. We surveyed 1,782 Internet users about risks associated with the capabilities of popular wearable devices on the market in order to identify risks that users find concerning. Our study  relatively ranks a range of potential wearables data capture scenarios, investigates the impact of the recipient of the data on the perceived risk of data capture, and explores the landscape users' concerns associated with wearable devices (including privacy and security, but also including factors such as increased safety risk, changes in social behaviors, and how wearable devices are unfashionable). To our knowledge, this is the largest user-based experiment concerning security and privacy concerns regarding wearables. We hope that this work will inform the community about user perceptions of wearable devices and aid in the design of future user notification, permission management, and access control schemes for wearables.
\end{abstract}

@@

Wearable devices enable benefits ranging from a fitness-data inspired lifestyle to an virtual-object filled augmented reality. However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Although wearable devices are still in their infancy, we have already seen manifestations of these risks. Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}. Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, but still resulted in tech hate crimes against its users ~\cite{1_russell_2014, 16_gross_2014}.

@@

The goal of this work is to motivate research on the still-malleable future of wearable interaction models to preserve privacy and security, which we found are the top user perceived risk associated with wearable devices.  Our survey of 1,782 Internet users contributes the following: %\\[-0.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We give a relative ranking of 72 potential wearables capture scenarios, which were inspired from the capabilities from the most popular wearable devices on the market at the time of the study. 
\item We study 4 possible data recipients to find that the recipient of the data contributes to the magnitude of overall perceived risk, but do not find statistically significant correlated factors of risk between data and recipient. 
\item We sketch a landscape of users' self-reported concerns regarding wearable devices and analyze responses using logistic regression models. 
\end{itemize}

\section{Methodology}
We designed a survey for our IRB-approved study to capture the general public's perception of wearables risks. To determine which of the current data capture scenarios were most concerning to users, we asked them to rate their level of concern for a handful of scenarios from a list of possible scenarios. This was intended to elicit their perception of the severity and impact of the risk. The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices~\cite{Felt}. To get a qualitative, unbounded measurement of what people thought the most common risk associated with wearables are, we ask our participants an open-ended question.

To obtain a representative list of scenarios, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market. At the time of this study (August 2014) the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc. These devices' capabilities and requested permissions were the basis for the list of possible data capture scenario questions used in this study, which we feel will be representative of what users are likely to encounter today.

\subsection{Survey Questions}
\noindent Each participant answered 27 questions across 5 sections:  \\[-.5cm]

@@

To assist in user fatigue, gave our participants a randomly selected subset of wearables scenarios. The average survey completion time was 11.5 minutes, which includes time for answering questions that are omitted from this paper due to lack of participants' familiarity with specific wearables devices and a misguided attempt to directly compare smartphones and wearables. See Appendix \ref{sec:noquestions} for details.

@@

\subsubsection{Wearable Scenarios}
We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., how much you exercise) was shared without permission with a particular recipient (e.g., work contacts). The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient. Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset'').. Figure \ref{fig:prompt}) shows an example.  Specifically, questions were of the form:

@@

We combined 72 data types (<data>) with 4 data recipients (<recipient>) to form an initial pool of 288 questions.We randomly pick 6 wearables scenarios from a list of 288 scenarios, and also display them to the user in a random order. Our 288 scenarios are the result of permuting 72 scenarios with 4 recipients, which can be seen in Table \ref{all-vur}. We clarified for our participants that ``app'' meant the the app's server, and that the data was not shared with anyone else. Each participant answered 6 questions that were randomly drawn from this pool.

\subsubsection{Additional Questions}
The exit portion of the survey contained demographic questions asking for age, gender, and education. We then asked about wearables ownership so we could control for prior exposure. An open-ended question on what would be the most likely risks associated with wearable devices was included to catch user concerns more broadly. To avoid biasing the open-ended question, we asked before concluding with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, which was included so we could control for participants' general privacy attitudes. However, we do realize that we asked this open-ended question after we had exposed our participants to a variety of wearables scenarios, which may have heightened their awareness of the possible risks. We talk about this more in Section 4.

@@

In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario.  The VUR is defined as the percentage of participants who reported a `5' on the Likert scales. 
We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced. Additionally, most people are likely to be upset, at least a little, in all scenarios, because a device is taking action without permission (rating distribution: ``1''= 759, ``2'' = 918, ``3'' = 1,452, ``4''' = 2,421, ``5'' = 8,344). Thus, the distinguishing factor is whether a participant was maximally upset, rather than if they were upset. A limitation of this approach is that it only allows us to make {\it relative} comparisons between scenarios, rather than being able to definitively state how upset people might be if a single scenario were to occur.

@@

The statistical significance arises for two distinct reasons. Firstly, sharing data only with an application's server carries less social impact. And for our participants, it may seem that it is shared with less people. Additionally, there is a class of data which may be considered odd for a human to know, but completely normal for a wearable device to know (e.g., it's okay if your fitbit knows when you sleep, but maybe less so for your friends).

@@

However, we do not claim that there are no distinctions between the friends, public, and work contact recipients. People are more comfortable sharing certain data types with certain human recipients. For instance, participants were significantly uncomfortable sharing if they were lying, nervous, or stressed to work contacts compared to the rest of the data recipients.Table \ref{all-vur} shows the  complete VUR and rankings of all data types by recipient.\\

@@

The participants were presented with a blank box to write in, with no particular suggestion on what to talk about, and with no character limit to their open-ended responses. Table \ref{openresponses} shows common user concerns related to wearable devices. Appendix \ref{sec:coding} details the responses categorized in each coding label. Note that participants were especially concerned with privacy and security, however, we do realize that we asked this open-ended question after we had exposed our participants to a variety of wearables scenarios, which may have heightened their awareness of the possible privacy and security risks.

\begin{quotation}
\noindent
\textit{P246: ``Privacy and security of your data, particularly for eg, stored financial/payment or medical information''}\\

@@

@@

\noindent
\textit{P1425: I think the biggest risk is how they may effect society as a whole... a wearable technology that's always on and available may push things even further to the point where people spend less time actually interacting with loved ones, and applying their own critical thinking in certain situations, instead always relying on their devices.}
\end{quotation}

The landscape of users' perceived risks associated with wearable devices are broad, encompassing concepts such as privacy and security, but also non-technical aspects such as health, safety, and change in social behaviors. We hope that this motivates researchers to investigate these aforementioned risks. \\

@@

\noindent {\bfseries Demographics Factors}
We see that privacy is a main concern for wearables users. Additionally, we show that privacy preferences should also be a consideration for configuring a user's device. A participant's self-reported level of privacy concerns is the biggest demographic predictor of participants' VUR rate. This is determined by the IUIPC scale~\cite{malhotra2004internet}. A Spearman correlation yielded a statistically significant effect between average IUIPC scores and VUR ($\rho=0.446$, $p<0.0005$), which suggests responses to questions were mostly based on privacy preferences. Additionally, we observed that age was another significant predictor of VUR ($\rho=0.121$, $p<0.0005$), but we suspect that this effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$). Others have observed that older individuals tend to be more privacy protective~\cite{varian2005demographics}.

@@

With regard to the presented risks, we observed that average VURs were highest for financial information disclosure (82.0\%). Information regarding relationships (69.2\%), physical safety (66.4\%), and self-image (65.8\%) followed. VURs were lowest for medical information disclosure (47.4\%). One reason why medical risks were ranked relatively low is that this category broadly covered scenarios involving data about the user's health, but also included more basic medical information, such as age, gender, and emotional state. As mentioned in Section \ref{sec:datatypes}, participants saw these as publicly observable and unconcerning.

@@

\noindent {\bfseries Limitations}
One of the limitations of our experiment is that our participants might not have knowledge or interest in wearables and their capabilities; 83\% of our participants reported that they do not own a wearable. Because of this, our participants may be over or underestimating the risk, stemming form an unawareness of what can be inferred from the data, not having clear relations of new technology with respect to familiar ones, and a higher likelihood of being influenced by reports of recent events.\footnote{Recently, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications~\cite{prabhakar2003biometric}. Our participants also did not differentiate between the benefits of risks of various new capabilities.

@@

Because of the privacy paradox, participants' stated responses may differ from how they may react to these same scenarios in real life~\cite{norberg2007privacy, jensen2005privacy}. At the same time, our results do reflect actual perceptions of wearable devices and the associated privacy scenarios involving them. This is an unavoidable, yet important distinction to make with of studies of this nature: our primary goal was to examine perceptions and preferences, so that future systems can be designed with these in mind. We do not expect that such systems will satisfy users in all situations, however, we believe that user-centered design will still be a vast improvement over post hoc approaches (or ignoring user concerns altogether).

Although we presented with our participants with a prompt illustrating all the benefits of a wearable, the questions we asked isolated from the risk from the benefits of sharing data with a particular recipient. We sacrificed context due to the complexity of the question necessary for the participant to answer correctly. Users are willing to tolerate risks if there is enough benefit associated with that risk. We do believe that since all of our questions were out of context, our study does represent what data people ambiguously would like to be private and secure, and is accurate for measuring user perceptions of wearables.\\

\noindent {\bfseries Future Research Directions}
We find that although people have opinions on applications which are familiar, users do not know the risk associated with new data or unfamiliar applications. We hope our work both informs the direction for future research to secure video, audio, and other currently considered sensitive sensor input channels, but also encourage work for contextual and user-input- independent permission models and access control schemes.

@@

\noindent {\bfseries Lessons form Smartphones} Smartphones allow applications to access new types of data. While this tends to benefit users, they do not think of the privacy implications. Lindqvist {\it et al.}\  studied a popular location tracking application, and found that people share their location information for gaming, signaling availability to friends, without concern for the privacy implications of broadcasting that information~\cite{lindqvist2011m}. There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}.

@@

 Our survey of 1,784 Internet users, is the first large-scale study to investigate user-centric security and privacy concerns for wearable devices. We contribute a comprehensive ranking of possible risks associated with wearable devices, across various recipients. We calibrate our results with mobile devices and existing technologies; additionally, we verify with an open-ended question and find that privacy and security are at the top of user's overall concerns. Wearables are still in their infancy. Perceptions of situations and capabilities will change rapidly with advancements and increased exposure. However, there is not much work done to determine which threats in the emerging threat landscape are pertinent to focus on. Inspection of possible data concerns agree with previous studies of smartphone studies to find that video capture and financial data to be most sensitive. Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous. We also find that users' self-reported privacy preferences are correlated with how participants may react, even with respect to situations that they are unfamiliar with. Permissions and access control mechanisms which do not depend on user inputs can still benefit from being informed by user preferences. We hope that this work has given a comprehensive overview of user concerns and inform designs of future privacy and security work for wearable devices.

>>>>

\begin{document}
\title{Risk Perceptions for Wearable Devices}
\numberofauthors{1}
\author{
 \alignauthor Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,3}, Joong Hwa Lee\textsuperscript{2}, David Wagner\textsuperscript{1}\\
   \vspace{0.5em}
   \affaddr{\textsuperscript{1}University of California, Berkeley, \{lnl,egelman,daw\}@cs.berkeley.edu}, \textsuperscript{2}dlwndghk94@berkeley.edu\\
   \affaddr{\textsuperscript{3}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
}

\maketitle

\begin{abstract}
\indent\indent Wearable devices, or ``wearables,'' bring great benefits but also potential risks that could expose users' activities without their awareness or consent. We surveyed 1,782 Internet users about risks associated with the capabilities of popular wearable devices on the market in order to identify risks that users find concerning. Our study relatively ranks a range of potential data capture scenarios enabled by wearable devices, investigates the impact of the recipient of the data on the perceived risk of data capture, and explores the landscape of users' concerns associated with wearable devices (including privacy and security, but also including factors such as increased safety risk, changes in social behaviors, and how wearable devices are unfashionable). To our knowledge, this is the largest user-based experiment concerning security and privacy concerns regarding wearables. We hope that this work will inform the community about user perceptions of wearable devices and aid in the design of future user notification, permission management, and access control schemes for wearables.
\end{abstract}

@@

Wearable devices enable benefits ranging from a fitness-data inspired lifestyle to a virtual-object filled augmented reality. However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Although wearable devices are still in their infancy, we have already seen manifestations of these risks. Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}. Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, but still resulted in tech hate crimes against its users ~\cite{1_russell_2014, 16_gross_2014}.

@@

The goal of this work is to motivate research on the still-malleable future of wearable interaction models to preserve privacy and security, which we found are the top user perceived risks associated with wearable devices.  Our survey of 1,782 Internet users contributes the following: %\\[-0.8cm]

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We give a relative ranking of 72 potential capture scenarios, which were inspired from the capabilities from the most popular wearable devices on the market at the time of the study. 
\item We study 4 possible data recipients to find that the recipient of the data contributes to the magnitude of overall perceived risk, but do not find statistically significant correlated factors of risk between data and recipient. 
\item We sketch a landscape of users' self-reported concerns regarding wearable devices and analyze responses using logistic regression models. 
\end{itemize}

\section{Methodology}
We designed a survey for our IRB-approved study to capture the general public's perception of wearables risks. To determine which of the current data capture scenarios were most concerning to users, we asked them to rate their level of concern for a handful of scenarios from a list of possible scenarios. This was intended to elicit their perception of the severity and impact of the risk. The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices~\cite{Felt}. To get a qualitative, unbounded measurement of what people thought the most common risk associated with wearables are, we asked our participants an open-ended question.

To obtain a representative list of scenarios, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market. At the time of this study (August 2014), the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks such as search, reading emails, etc. These devices' capabilities and requested permissions were the basis for the list of possible data capture scenario questions used in this study, which we feel will be representative of what users are likely to encounter today.

\subsection{Survey Questions}
\noindent We report on participants' responses to 23 questions across 4 survey sections:  \\[-.5cm]

@@

To reduce fatigue, we gave our participants a randomly selected subset of wearables scenarios. The average survey completion time was 11.5 minutes, which includes four questions that we omitted from this paper due to lack of participants' familiarity with specific devices and a misguided attempt to directly compare smartphones and wearables. See Appendix \ref{sec:noquestions} for details.

@@

\subsubsection{Wearable Scenarios}
We presented scenarios involving data captured by the Cubetastic3000 and asked participants to rate how upset they would be if a particular type of data (e.g., how much you exercise) was shared without permission with a particular recipient (e.g., work contacts). The purpose for using this question format was to determine how upset participants would be if data were inappropriately shared, and the extent to which their reactions were based on the data type and recipient. Responses were reported on a 5-point Likert scale (from ``indifferent'' to ``very upset''). Figure \ref{fig:prompt} shows an example.  Specifically, questions were of the form:

@@

We combined 72 data types (<data>) with 4 data recipients (<recipient>) to form a pool of 288 scenarios (Table \ref{all-vur}). Each participant answered 6 questions that were randomly drawn from this pool, displayed in random order. We clarified for our participants that ``app'' meant the app's server, and that the data was not shared with anyone else.

\subsubsection{Additional Questions}
The exit portion of the survey contained demographic questions (age, gender, and education), and then asked about wearable device ownership so we could control for prior exposure. An open-ended question on what would be the most likely risks associated with wearable devices was included to capture user concerns more broadly. To avoid biasing the open-ended question, we asked before concluding with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, which was included so we could control for participants' general privacy attitudes. However, we do realize that we asked this open-ended question after we had exposed our participants to a variety of wearables scenarios, which may have heightened their awareness of the possible risks. We talk about this more in Section 4.

@@

In performing our analysis in the next section, we chose to focus on the very upset rate (VUR) of each scenario~\cite{Felt}.  The VUR is defined as the percentage of participants who reported a `5' on the Likert scales. 
We use the VURs rather than the average of all Likert scores for the same reasons as Felt {\it et al.}: the VUR does not presume that the ratings, ranging from ``indifferent'' to ``very upset,'' are linearly spaced. Additionally, most people are likely to be upset, at least a little, in all scenarios, because a device is taking action without permission (rating distribution: ``1''= 759, ``2'' = 918, ``3'' = 1,452, ``4''' = 2,421, ``5'' = 8,344). Thus, the distinguishing factor is whether a participant was maximally upset. A limitation of this approach is that it only allows us to make {\it relative} comparisons between scenarios, rather than being able to definitively state how upset people might be if a single scenario were to occur.

@@

The statistical significance arises for two distinct reasons. Firstly, sharing data only with an application's server carries less social impact. And for our participants, it may seem that it is shared with fewer people. Additionally, there is a class of data which may be considered odd for a human to know, but completely normal for a wearable device to know (e.g., it's okay if your Fitbit knows when you sleep, but maybe less so for your friends).

@@

However, we do not claim that there are no distinctions between the friends, public, and work contact recipients. People are more comfortable sharing certain data types with certain human recipients. For instance, participants were significantly more uncomfortable sharing if they were lying, nervous, or stressed to work contacts compared to the rest of the data recipients. Table \ref{all-vur} shows the complete VURs and rankings of all data types by recipient.\\

@@

The participants were presented with a blank box to write in, with no particular suggestion on what to talk about, and with no character limit to their open-ended responses. Table \ref{openresponses} shows common user concerns related to wearable devices. Appendix \ref{sec:coding} details the responses categorized in each coding label. Note that participants were especially concerned with privacy and security, however, we do realize that we asked this open-ended question after we had exposed our participants to a variety of privacy-related scenarios, which may have heightened their awareness of the possible privacy and security risks.

\begin{quotation}
\noindent
\textit{P246: ``Privacy and security of your data, particularly for eg, [sic] stored financial/payment or medical information''}\\

@@

\end{quotation}

@@

\begin{quotation}
\noindent
\textit{P1425: I think the biggest risk is how they may effect society as a whole... a wearable technology that's always on and available may push things even further to the point where people spend less time actually interacting with loved ones, and applying their own critical thinking in certain situations, instead always relying on their devices.}
\end{quotation}

The landscape of users' perceived risks associated with wearable devices is broad, encompassing concepts such as privacy and security, but also non-technical aspects such as health, safety, and change in social behaviors. We hope that this motivates researchers to investigate these aforementioned risks. \\

@@

\noindent {\bfseries Demographics Factors}
We see that privacy is a main concern for wearables users. Additionally, we show that privacy preferences should also be a consideration when configuring a user's device. A participant's self-reported level of privacy concern---as determined by the IUIPC scale~\cite{malhotra2004internet}---is the biggest demographic predictor of VURs. A Spearman correlation yielded a statistically significant effect between average IUIPC scores and average VUR ($\rho=0.446$, $p<0.0005$), which suggests responses to questions were mostly based on privacy preferences. Additionally, we observed that age was another significant predictor of VUR ($\rho=0.121$, $p<0.0005$), but we suspect that this effect is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$). Others have observed that older individuals tend to be more privacy protective~\cite{varian2005demographics}.

@@

With regard to the presented risks, we observed that average VURs were highest for financial information disclosure (82.0\%). Information regarding relationships (69.2\%), physical safety (66.4\%), and self-image (65.8\%) followed. VURs were lowest for medical information disclosure (47.4\%). One reason why medical risks were ranked relatively low is that this category broadly covered scenarios involving data about the user's health, but also included more basic medical information, such as age, gender, and emotional state. As mentioned earlier, participants saw these as publicly observable and therefore unconcerning.

@@

\noindent {\bfseries Limitations}
One of the limitations of our experiment is that our participants might not have knowledge or interest in wearables and their capabilities; 83\% of our participants reported that they do not own a wearable. Because of this, our participants may be over or underestimating the risk, stemming from an unawareness of what can be inferred from the data, not having clear relations of new technology with respect to familiar ones, and a higher likelihood of being influenced by reports of recent events.\footnote{At the time of the survey, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  For instance, biometrics were generally not a concern for our participants, although there are many security and privacy implications~\cite{prabhakar2003biometric}. Our participants also did not differentiate between the benefits and risks of various new capabilities.

@@

Because of the privacy paradox, participants' stated responses may differ from how they may react to these same scenarios in real life~\cite{norberg2007privacy, jensen2005privacy}. At the same time, our results do reflect actual perceptions of wearable devices and the associated privacy scenarios involving them. This is an unavoidable, yet important distinction to make with of studies of this nature: our primary goal was to examine perceptions and preferences, so that future systems can be designed with these in mind. We do not expect that such systems will satisfy users in all situations, however, we believe that user-centered design will still be a vast improvement over {\it post hoc} approaches (or ignoring user concerns altogether).

Although we presented our participants with a prompt illustrating all the benefits of a wearable device, the questions we asked isolated the risk from the benefits of sharing data with a particular recipient. We sacrificed context due to the complexity of the question necessary for the participant to answer correctly. Users are willing to tolerate risks if there is enough benefit associated with that risk. We do believe that since all of our questions were out of context, our study does represent what data people ambiguously would like to be private and secure, and is accurate for measuring user perceptions of wearables.\\

\noindent {\bfseries Future Research Directions}
We find that although people have opinions on applications which are familiar, users do not know the risk associated with new data or unfamiliar applications. We hope our work both informs the direction for future research to secure video, audio, and other currently considered sensitive sensor input channels, but also encourages work for contextual and user-input-independent permission models and access control schemes.

@@

\noindent {\bfseries Lessons from Smartphones} Smartphones allow applications to access new types of data. While this tends to benefit users, they do not think of the privacy implications. Lindqvist {\it et al.}\  studied a popular location tracking application, and found that people share their location information for gaming, signaling availability to friends, without concern for the privacy implications of broadcasting that information~\cite{lindqvist2011m}. There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}.

@@

 Our survey of 1,784 Internet users is the first large-scale study to investigate user-centric security and privacy concerns for wearable devices. We contribute a comprehensive ranking of possible risks associated with wearable devices, across various recipients. Our open-ended responses show that privacy and security are at the top of user's overall concerns. While wearables are still in their infancy, perceptions of situations and capabilities are likely to change rapidly with advancements and increased exposure. However, there has not been much prior work done to determine which threats in the emerging threat landscape are pertinent to focus on. Our examination of possible data concerns agree with previous studies of smartphone users that found that video capture and financial data are the most sensitive data types. Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous. We also found that users' self-reported privacy preferences are correlated with how they may react, even with respect to situations that they are unfamiliar with. Our results may be used by system designers to create permissions and access control mechanisms that do not directly depend on users' inputs. We hope that this work has given a comprehensive overview of user concerns and informs designs of future privacy and security work for wearable devices.
